---
title: "HODP_R_Bootcamp"
author: "Vanessa + Jason"
date: "10/14/2020"
output: pdf_document
---

First checking the dataset as a whole
```{r}
df <- read.csv("MuseumDataFull.csv")
summary(df)
```

EDA of totaluniquepageviews
Extremely right skewed
```{r}
names(df)[names(df) == "totaluniquepageviews"] <- "views"
hist(df$views, breaks = 500)
hist(df$views, breaks = 500, xlim = c(0, 5000))
hist(df$views, breaks = 5000, xlim = c(0, 500))
hist(df$views, breaks = 5000, xlim = c(0, 500), ylim = c(0, 100))
hist(df$views, breaks = 5000, xlim = c(0, 200))

max(df$views) #max = 13079
df[which.max(df$views),]
summary(df$views)
quantile(df$views, c(0:20)/20)
sum(df$views > 100) #421
```

EDA of culture
Some weird stuff, like with "European?"
multiple categories of Italian, Roman, Spanish, British; there is Flemish and Franco-Flemish and French
Unidentified culture and unknown are also two categories
"Graeco-Bactrian"              
"Graeco-Roman" + "Greek"
"Hellenistic"                  
"Hellenistic or Early Roman" 

```{r}
# broader stroke, 21 categories
head(df$culture)
allcnames <- unique(df$culture)
length(allcnames)
orderedcnames <- allcnames[order(allcnames)]
orderedcnames
# first remove the question marks, kinda pointless here
df$culture <- gsub("[?]", "", df$culture)

# Make consistent different locations
df$culture <- gsub("^British.+", "British", df$culture)
df$culture <- gsub("^Italian.+", "Italian", df$culture)
df$culture <- gsub("^Roman.+", "Roman", df$culture)
df$culture <- gsub("^Spanish.+", "Spanish", df$culture)

df$culture[df$culture == "" | df$culture == "Unidentified culture"  | df$culture == "unknown"] <- "Unknown"

length(unique(df$culture))

# boarder stroke, 20 categories
df$fculture <- df$culture
culturerank <- names(which(table(df$culture) > 50))
length(culturerank)
df$fculture[!df$culture %in% culturerank] <- "Other"
table(df$fculture)
df$fculture <- as.factor(df$fculture)
plot(df$fculture, las = 2)

# smaller stroke, 10 categories
df$ffculture <- df$culture
culturerank <- names(which(table(df$culture) > 500))
length(culturerank)
df$ffculture[!df$culture %in% culturerank] <- "Other"
table(df$ffculture)
df$ffculture <- as.factor(df$ffculture)
plot(df$ffculture, las = 2)
```

oh god, the dated stuff will be very annoying to clean
```{r}
library(stringr)
head(df$dated)

# get rid of those unknown stuff
uuu <- str_detect(df$dated, "^[Uu]")
allunknown <- c(unique(df$dated[uuu]), "")
sum(df$dated == "Unknown")
df$dated[df$dated %in% allunknown] <- "Unknown"

# lowkey lumping all the BCE together, as not too many of them
bce <- str_detect(df$dated, "BCE")
sum(df$dated[bce])
df$dated[bce] <- "BCE"

# then hopefully can lump by century GG
# first work with the best case scenario LOL
# thank u random guy: https://gist.github.com/micstr/69a64fbd0f5635094a53
IsDate <- function(mydate, date.format = "%m/%d/%y") {
  tryCatch(!is.na(as.Date(mydate, date.format)),  
           error = function(err) {FALSE})  
}

nicedates <- IsDate(df$dated)
sum(nicedates)
a = c("asd", "acs", "asd")
substr(a, 1, 2)
head(df$dated)
unique(df$dated)
sum(df$dated == "Unknown")
```

