---
title: "HODP_R_Bootcamp"
author: "Vanessa + Jason"
date: "10/14/2020"
output: pdf_document
---

```{r}
source('styleguide.R')
```


# Check Dataset as a Whole
```{r}
df <- read.csv("./MuseumDataFull1015.csv")
summary(df)
theme_set(theme_hodp())
```

## EDA of totaluniquepageviews

Extremely right skewed
```{r}
names(df)[names(df) == "totaluniquepageviews"] <- "views"
hist(df$views, breaks = 500)
hist(df$views, breaks = 500, xlim = c(0, 5000))
hist(df$views, breaks = 5000, xlim = c(0, 500))
hist(df$views, breaks = 5000, xlim = c(0, 500), ylim = c(0, 100))
hist(df$views, breaks = 5000, xlim = c(0, 200))

max(df$views) #max = 3234
df[which.max(df$views),]
summary(df$views)
quantile(df$views, c(0:20)/20)
sum(df$views > 100) #400
```

## EDA of Culture
Some weird stuff, like with "European?"
multiple categories of Italian, Roman, Spanish, British; there is Flemish and Franco-Flemish and French
Unidentified culture and unknown are also two categories
"Graeco-Bactrian"              
"Graeco-Roman" + "Greek"
"Hellenistic"                  
"Hellenistic or Early Roman" 

### Add general culture labels
```{r}
# broader stroke, 21 categories
head(df$culture)
allcnames <- unique(df$culture)
length(allcnames)
orderedcnames <- allcnames[order(allcnames)]
#orderedcnames
# first remove the question marks, kinda pointless here
df$culture <- gsub("[?]", "", df$culture)

# Make consistent different locations using regex
df$culture <- gsub("^British.+", "British", df$culture)
df$culture <- gsub("^Italian.+", "Italian", df$culture)
df$culture <- gsub("^Roman.+", "Roman", df$culture)
df$culture <- gsub("^Spanish.+", "Spanish", df$culture)
df$culture <- gsub("^German\\?", "German", df$culture)
df$culture <- gsub("^European.+", "European", df$culture)
df$culture <- gsub("^$", "Unknown", df$culture)

df$culture[df$culture == "^$" | df$culture == "Unidentified culture"] <- "Unknown"

length(unique(df$culture))
df %>% select(culture)
```

#### Dataframes for top 20 or 10 cultures


```{r}
# broader stroke, 20 categories
df$fculture <- df$culture
culturerank <- names(which(table(df$culture) > 50))
length(culturerank)
df$fculture[!df$culture %in% culturerank] <- "Other"
table(df$fculture)
df$fculture <- as.factor(df$fculture)
plot(df$fculture, las = 2)
head(df)
#df %>% select(title,fculture)


# length(df)
```


```{r}
# smaller stroke, 10 categories
df$ffculture <- df$culture
culturerank <- names(which(table(df$culture) > 500))
length(culturerank)
df$ffculture[!df$culture %in% culturerank] <- "Other"
table(df$ffculture)
df$ffculture <- as.factor(df$ffculture)
plot(df$ffculture, las = 2)
```

# EDA: Department, Division, Century, Period
```{r}
head(df$department)
unique(df$department)
df$department <- as.factor(df$department)
head(df$division)
length(unique(df$division))
unique(df$division)
df$division[df$division == ""] <- "Other"
df$division <- as.factor(df$division)
plot(df$division, las = 2)
head(df$period)
length(unique(df$period))
head(df$century)
length(unique(df$century))
#unique(df$century)
head(df$dateend)
hist(df$rank)
hist(df$accessionyear)
#plot()
```

# EDA: Datethings

```{r}
hist(df$dateend, breaks = 300)
sum(df$dateend == 0)
sum(df$datebegin == 0 & df$dateend == 0)
head(df$century[df$datebegin == 0 & df$dateend == 0])
#making rank something reasonable
hist(df$rank, breaks = 300)
summary(df$rank)
plot(rank ~ views, data = df)
df$arank <- df$rank
df$arank <- df$arank - min(df$arank) + 1
df$arank <- df$arank / (max(df$arank) + 1)
df$arank <- log(df$arank / (1 - df$arank))


#making logviews something reasonable
df$logviews <- log(df$views + 1)

df_validdates <- df[df$datebegin != 0 | df$dateend != 0,]
df_validdates$meddate <- (df_validdates$datebegin + df_validdates$dateend) / 2
hist(df_validdates$meddate, breaks = 300)
#df_validdates$meddate
# lm1 <- lm(views ~ meddate, data = df_validdates)
# summary(lm1)
# plot(lm1)
```

## Data Analysis

Recommend do geom_violin:
ex: tweet_data %>% ggplot(aes(x = about_china, y = sentiment)) + geom_violin(trim = FALSE, aes(fill = about_china), alpha = 0.8) + xlab("Tweet Type") + ylab("Sentiment") + scale_fill_discrete(name = "Tweet Type", labels = ch_cats) + scale_x_discrete(labels=ch_cats) + ggtitle("China-Related Tweet Sentiment Distribution") + theme_minimal() + ggsave("violin_ch.png", width = 5, height = 5)
```{r}
df_validdates$logdate <- log(max(df_validdates$meddate) - df_validdates$meddate + 1)
hist(df_validdates$logdate)
hist(df_validdates$logviews)
summary(df_validdates$logviews)

lm2 <- lm(logviews ~ logdate, data = df_validdates)
summary(lm2)
plot(logviews ~ logdate, data = df_validdates)
abline(lm2, col = "Blue")
plot(lm2, which = c(1, 2)) #assumptions really not met

boxplot(views ~ ffculture, data = df)
#boxplot(logviews ~ ffculture, data - df)
```


# final analyses
```{r}
boxplot(views ~ ffculture, data = df)
hist(df$logviews)
boxplot(logviews ~ ffculture, data = df)
summary(aov(logviews~ ffculture, data = df))
tapply(df$views, df$ffculture, var)

hist(df$accessionyear)
plot(views ~ accessionyear, data = df)

lo1 <- loess(views ~ accessionyear, data = df, span = 1)
sampyear <- 1700:2020
yhat <- predict(lo1, newdata = data.frame(accessionyear = sampyear))
plot(views ~ accessionyear, data = df)
lines(yhat ~ sampyear, col = "red", lwd = 2)

lo2 <- loess(views ~ accessionyear, data = df[-which.min(df$accessionyear),], span = 1)
sampyear <- 1850:2020
yhat <- predict(lo2, newdata = data.frame(accessionyear = sampyear))
plot(views ~ accessionyear, data = df[-which.min(df$accessionyear),])
lines(yhat ~ sampyear, col = "red", lwd = 2)



lo2 <- loess(logviews ~ accessionyear, data = df[-which.min(df$accessionyear),], span = 1)
sampyear <- 1850:2020
yhat <- predict(lo2, newdata = data.frame(accessionyear = sampyear))
plot(logviews ~ accessionyear, data = df[-which.min(df$accessionyear),])
lines(yhat ~ sampyear, col = "red", lwd = 2)
```

```{r}
poislm <- glm(views ~ accessionyear, data = df[-which.min(df$accessionyear),], family = "poisson")
summary(poislm)

lm123 <- lm(logviews ~ accessionyear, data = df[-which.min(df$accessionyear),])
summary(lm123)
```


```{r}
plot(rank ~ logdate, data = df_validdates)
plot(arank ~ logdate, data = df_validdates)
lm3 <- lm(arank ~ logdate, data = df_validdates)
summary(lm3)
plot(lm3, which = c(1, 2))
```

EDA: Intersections
```{r}
plot(df$views ~ df$division, las = 2)
```


oh god, the dated stuff will be very annoying to clean
```{r, eval = F}
library(stringr)
head(df$dated)

# get rid of those unknown stuff
uuu <- str_detect(df$dated, "^[Uu]")
allunknown <- c(unique(df$dated[uuu]), "")
sum(df$dated == "Unknown")
df$dated[df$dated %in% allunknown] <- "Unknown"

# lowkey lumping all the BCE together, as not too many of them
bce <- str_detect(df$dated, "BCE")
sum(df$dated[bce])
df$dated[bce] <- "BCE"

# then hopefully can lump by century GG
# first work with the best case scenario LOL
# thank u random guy: https://gist.github.com/micstr/69a64fbd0f5635094a53
IsDate <- function(mydate, date.format = "%m/%d/%y") {
  tryCatch(!is.na(as.Date(mydate, date.format)),  
           error = function(err) {FALSE})  
}

nicedates <- IsDate(df$dated)
sum(nicedates)
a = c("10/2/2020", 13, "asd")
a[1] <- as.Date(a[1])
substr(a, 1, 2)
head(df$dated)
unique(df$dated)
sum(df$dated == "Unknown")
```


## Plots/Visualizations
```{r}

# example
# https://github.com/HarvardOpenData/HODP-StyleGuide/blob/master/ggplot_example.R

# Add logo
#grid::grid.raster(logo, x = 0.01, y = 0.01, just = c('left', 'bottom'), width = unit(2, 'cm'))

# Interactive Graphic
#ggplotly(a)
```

```{r}
library(ggplot2)
df <- as.data.frame(df)

#barplot of all the cultures
df$ffculture <- reorder(df$ffculture, df$ffculture, FUN = length)
ggplot(data =df, aes(x = ffculture)) + geom_bar() + 
  labs(y = "Occurrences Per Culture", x = "Cultures", title = "Barplot of Cultures")

#accessionyear vs views
ggplot(data = df, aes(x = accessionyear, y = views)) + geom_point()
typeof(df)

#culture vs views
# bar plot
cultureviews <- aggregate(df$views, by = list(df$ffculture), FUN = mean)
colnames(cultureviews) <- c("Culture", "Views")
cultureviews <- cultureviews[order(cultureviews$Views),]
cultureviews$Culture <- factor(cultureviews$Culture, levels = cultureviews$Culture)
ggplot(data = cultureviews, aes(x= Culture, y = Views)) + geom_bar(stat = "identity") + 
  labs(y = "Average Views Per Culture", title = "Boxplot of Average Views Per Culture")

#dot plot
ggplot(cultureviews, aes(x=Culture, y=Views)) + 
  geom_point(col = '#EE3838', size=3) +   # Draw points
  geom_segment(aes(x=Culture, 
                   xend=Culture, 
                   y=min(Views), 
                   yend=max(Views)), 
               linetype="dashed", 
               size=0.1) +   # Draw dashed lines
  labs(title="Dot Plot of Average Vies Per Culture", 
       subtitle="", 
       caption="") +  
  coord_flip()

#boxplots
ggplot(df, aes(x=ffculture, y=views)) +
  geom_boxplot()
ggplot(df, aes(x=ffculture, y=logviews)) +
  geom_boxplot()


#culture vs ranks: boxplots
cultureranks <- aggregate(df$rank, by = list(df$ffculture), FUN = mean)
colnames(cultureranks) <- c("Culture", "Ranks")
cultureranks <- cultureranks[order(cultureranks$Ranks),]
cultureranks$Culture <- factor(cultureranks$Culture, levels = cultureranks$Culture)
ggplot(data = cultureranks, aes(x= Culture, y = Ranks)) + geom_bar(stat = "identity") + 
  labs(y = "Average Ranks Per Culture", title = "Boxplot of Average Ranks Per Culture")


# culture and rank boxplots
df$ffculture <- factor(df$ffculture, levels = c("Japanese", "Greek", "Roman", "Other", "American", "German", "Unknown", "British", "Italian", "French"))
ggplot(df, aes(x=ffculture, y=rank)) +
  geom_boxplot() + scale_y_reverse() + labs(y = "Rank", x = "Culture",
  title = "Boxplots of Culture Ranks")

```
