---
title: "HODP_R_Bootcamp"
author: "Vanessa + Jason"
date: "10/14/2020"
output: pdf_document
---

We first upload the styleguide like usual.
```{r}
source('./styleguide.R')
```


### Check Dataset as a Whole
We first load the data and then look at the summary in order to see if we need to transform any variables.
```{r}
df <- read.csv("./MuseumDataFull1015.csv")
summary(df)
theme_set(theme_hodp())
```

### EDA of Views
We first do some EDA for uniquepageviews, in order to better understand the distribution of views. Note that it is extremely right skewed.
```{r}
names(df)[names(df) == "totaluniquepageviews"] <- "views"
hist(df$views, breaks = 500)
hist(df$views, breaks = 500, xlim = c(0, 5000))
hist(df$views, breaks = 5000, xlim = c(0, 500))
hist(df$views, breaks = 5000, xlim = c(0, 500), ylim = c(0, 100))
hist(df$views, breaks = 5000, xlim = c(0, 200))

max(df$views) #max = 3234
df[which.max(df$views),] #looking at the maximum value
summary(df$views)
quantile(df$views, c(0:20)/20) #a lot of the points do not have over 100 views
sum(df$views > 100) #400 of them have more than 100 views
#making logviews something reasonable
df$logviews <- log(df$views + 1)
```

### EDA of Culture
There are some weird occurrences, like with "European?". For the sake of simplicity, I would remove all of the question marks at the end.
There were also multiple categories of Italian, Roman, Spanish, British.
There are a few culture groups like Flemish, Franco-Flemish, and French, as well as "Graeco-Bactrian", "Graeco-Roman", and "Greek". For these, where some categories that intersect different cultures.
Unidentified culture and unknown are also two categories; both categories were merged together, alongside pieces that have their culture category as blank.

#### Filtering some cultures
```{r}
# broader stroke, 21 categories
head(df$culture)
allcnames <- unique(df$culture)
length(allcnames)
orderedcnames <- allcnames[order(allcnames)]
#orderedcnames
# first remove the question marks
df$culture <- gsub("[?]", "", df$culture)

# Make consistent different locations using regex
df$culture <- gsub("^British.+", "British", df$culture)
df$culture <- gsub("^Italian.+", "Italian", df$culture)
df$culture <- gsub("^Roman.+", "Roman", df$culture)
df$culture <- gsub("^Spanish.+", "Spanish", df$culture)
df$culture <- gsub("^German\\?", "German", df$culture)
df$culture <- gsub("^European.+", "European", df$culture)
df$culture <- gsub("^$", "Unknown", df$culture)

# merging together the different unknown cultures
df$culture[df$culture == "^$" | df$culture == "Unidentified culture"] <- "Unknown"

# looks at how many cultures remain
length(unique(df$culture)) #133 remain
head(df %>% select(culture)) # looking at a few of these cultures
```

#### Dataframes for top 20 or 10 cultures
As there are too many cultures, we decided to filter the culture categories a bit more. We first filter out those that have over 50 occurrences, and then shift the rest into Other.
```{r}
# broader stroke, 20 categories
df$fculture <- df$culture
culturerank <- names(which(table(df$culture) > 50))
length(culturerank) # now only 19 named categories remain
df$fculture[!df$culture %in% culturerank] <- "Other" #the rest of the cultures are marked as other
table(df$fculture) #looks at the table of cultures
df$fculture <- as.factor(df$fculture)
plot(df$fculture, las = 2)
```

We now filter it even more, down to cultures that have over 500 categories. Now only 10 categories remain.
```{r}
# smaller stroke, 10 categories
df$ffculture <- df$culture
culturerank <- names(which(table(df$culture) > 500))
length(culturerank)
df$ffculture[!df$culture %in% culturerank] <- "Other"
table(df$ffculture)
df$ffculture <- as.factor(df$ffculture)
plot(df$ffculture, las = 2)
```

#### Export the clean data
```{r}
write.csv(df, 'cleanedData.csv')
```



#### EDA: Department, Division, Century, Period
This part can be skipped, as it was not used in the final article.
```{r}
#head(df$department)
#unique(df$department)
df$department <- as.factor(df$department)
#head(df$division)
#length(unique(df$division))
#unique(df$division)
df$division[df$division == ""] <- "Other"
df$division <- as.factor(df$division)
#plot(df$division, las = 2)
#head(df$period)
#length(unique(df$period))
#head(df$century)
#length(unique(df$century))
#unique(df$century)
#head(df$dateend)
#hist(df$rank)
#hist(df$accessionyear)
```

#### EDA: Datethings
This part can be skipped, as it was not used in the final article.
```{r}
#hist(df$dateend, breaks = 300)
#sum(df$dateend == 0)
#sum(df$datebegin == 0 & df$dateend == 0)
#head(df$century[df$datebegin == 0 & df$dateend == 0])
#making rank something reasonable
#hist(df$rank, breaks = 300)
#summary(df$rank)
#plot(rank ~ views, data = df)

#arank was an attempt to make the ranks more normally distributed
df$arank <- df$rank
df$arank <- df$arank - min(df$arank) + 1
df$arank <- df$arank / (max(df$arank) + 1)
df$arank <- log(df$arank / (1 - df$arank))


df_validdates <- df[df$datebegin != 0 | df$dateend != 0,]
df_validdates$meddate <- (df_validdates$datebegin + df_validdates$dateend) / 2
#hist(df_validdates$meddate, breaks = 300)
```

### Data Analysis: logdate vs logviews
This part can be skipped, as it was not used in the final article. 
```{r}
df_validdates$logdate <- log(max(df_validdates$meddate) - df_validdates$meddate + 1)
#hist(df_validdates$logdate)
#hist(df_validdates$logviews)
#summary(df_validdates$logviews)

#lm2 <- lm(logviews ~ logdate, data = df_validdates)
#summary(lm2)
#plot(logviews ~ logdate, data = df_validdates)
#abline(lm2, col = "Blue")
#plot(lm2, which = c(1, 2)) #assumptions really not met
```

## Views vs FFculture analysis
This part is used in the article. We usually assume in the ANOVA test, that we want normality and constant variance. This is why we need to use the transformed logviews instead of the original views. We can see this by comparing the side-by-side boxplots for views versus logviews. From looking at the variances for the transformed variances, we see that it is the difference between the largest and the smallest variance is about a factor of 2. The normality assumption does not seem to be satisfied, as the overall log-views is still right-skewed. But given the large sample size, it works.
```{r}
boxplot(views ~ ffculture, data = df)
tapply(df$views, df$ffculture, var)
hist(df$logviews)
boxplot(logviews ~ ffculture, data = df)
summary(aov(logviews~ ffculture, data = df))
tapply(df$logviews, df$ffculture, var)
```

### Data Analysis: accessionyear vs views
This part is not used in the article. So this can be skipped.
```{r}
#hist(df$accessionyear)
#plot(views ~ accessionyear, data = df)

#lo1 <- loess(views ~ accessionyear, data = df, span = 1)
#sampyear <- 1700:2020
#yhat <- predict(lo1, newdata = data.frame(accessionyear = sampyear))
#plot(views ~ accessionyear, data = df)
#lines(yhat ~ sampyear, col = "red", lwd = 2)

#loess models as assumptions are not met
#lo2 <- loess(views ~ accessionyear, data = df[-which.min(df$accessionyear),], span = 1)
#sampyear <- 1850:2020
#yhat <- predict(lo2, newdata = data.frame(accessionyear = sampyear))
#plot(views ~ accessionyear, data = df[-which.min(df$accessionyear),])
#lines(yhat ~ sampyear, col = "red", lwd = 2)

#lo2 <- loess(logviews ~ accessionyear, data = df[-which.min(df$accessionyear),], span = 1)
#sampyear <- 1850:2020
#yhat <- predict(lo2, newdata = data.frame(accessionyear = sampyear))
#plot(logviews ~ accessionyear, data = df[-which.min(df$accessionyear),])
#lines(yhat ~ sampyear, col = "red", lwd = 2)

# using a poisson regression as well as a normal linear regression
#poislm <- glm(views ~ accessionyear, data = df[-which.min(df$accessionyear),], family = "poisson")
#summary(poislm)

#lm123 <- lm(logviews ~ accessionyear, data = df[-which.min(df$accessionyear),])
#summary(lm123)
```


### Data Analysis: rank vs logdate
This part can also be skipped, as it was not used in the final article. 
```{r}
#plot(rank ~ logdate, data = df_validdates)
# used arank instead of rank
# arank was created before df_validdates; go to EDA: datethings to see how it was made


#plot(arank ~ logdate, data = df_validdates) 
#lm3 <- lm(arank ~ logdate, data = df_validdates)
#summary(lm3)
#plot(lm3, which = c(1, 2))
```


This was an attempt to clean up the original dates, but this was not used as well so this can be skipped.
```{r, eval = F}
library(stringr)
head(df$dated)

# get rid of those unknown stuff
uuu <- str_detect(df$dated, "^[Uu]")
allunknown <- c(unique(df$dated[uuu]), "")
sum(df$dated == "Unknown")
df$dated[df$dated %in% allunknown] <- "Unknown"

# lowkey lumping all the BCE together, as not too many of them
bce <- str_detect(df$dated, "BCE")
sum(df$dated[bce])
df$dated[bce] <- "BCE"

# then hopefully can lump by century GG
# first work with the best case scenario LOL
# thank u random guy: https://gist.github.com/micstr/69a64fbd0f5635094a53
IsDate <- function(mydate, date.format = "%m/%d/%y") {
  tryCatch(!is.na(as.Date(mydate, date.format)),  
           error = function(err) {FALSE})  
}

nicedates <- IsDate(df$dated)
sum(nicedates)
a = c("10/2/2020", 13, "asd")
a[1] <- as.Date(a[1])
substr(a, 1, 2)
head(df$dated)
unique(df$dated)
sum(df$dated == "Unknown")
```


## Visualizations
This is the more useful overall section. Admittedly, even here, some visualizations were not used.


#### Accession Year
This part is not used in the article. So this can be skipped.
```{r}
#accYear_views = df  %>% mutate(Culture=fculture) %>% ggplot(aes(x=accessionyear, y = views)) + geom_point(aes(color = Culture)) + ggtitle("Views and Accession Year") + xlab("Accession Year") + ylab("Average Views") + xlim(1890, 2020) + ggsave("./graphs/accYear_views.png", width = 7.5, height = 5)
#ggplot(data = df[-which.min(df$accessionyear),], aes(x = accessionyear, y = views)) + geom_point()
#accYear_views
grid::grid.raster(logo, x = 0.01, y = 0.01, just = c('left', 'bottom'), width = unit(2, 'cm'))
```



#### Filtered to Top 20 Cultures

This helps to create the later visuals.
```{r}
# change to > 50 for top 20
culturerank <- names(which(table(df$culture) > 500))
print(culturerank)
df20 = df %>% filter(ffculture %in% culturerank) %>% filter(!(as.character(ffculture) %in% c("Unknown")))
df20 %>% select(culture, title)
```


#### Prep data for visual, summary statistics
More preparation for visuals.
```{r}
dfCircle = df20 %>% group_by(culture) %>% summarize(n(), mean(views), median(views), sd(views), mean(rank), median(rank), sd(rank))
names(dfCircle)[names(dfCircle) == "n()"] <- "count"
names(dfCircle)[names(dfCircle) == "mean(views)"] <- "meanViews"
names(dfCircle)[names(dfCircle) == "median(views)"] <- "medViews"
names(dfCircle)[names(dfCircle) == "sd(views)"] <- "sdViews"
names(dfCircle)[names(dfCircle) == "mean(rank)"] <- "meanRank"
names(dfCircle)[names(dfCircle) == "median(rank)"] <- "medRank"
names(dfCircle)[names(dfCircle) == "sd(rank)"] <- "sdRank"
print(dfCircle)
```


#### Circle vis for Mean Views, and Count
This creates the circle plot in the article.
```{r}
### Mean Views
library(packcircles)

circleData <- data.frame(culture=dfCircle$culture, avgViews=dfCircle$meanViews) 
packing <- circleProgressiveLayout(circleData$avgViews, sizetype='area')
circleData <- cbind(circleData, packing)
dat.gg <- circleLayoutVertices(packing, npoints=50)
dat.gg$avgViews <- rep(circleData$avgViews, each=51)
#print(dat.gg)
circles = ggplot() + 
  
  geom_polygon(data = dat.gg, aes(x, y, group = id, fill=avgViews, color="D84742")) +
  scale_fill_continuous(high='#D84742', low='#FF9586') +
  
  geom_text(data = circleData, aes(x, y, size=avgViews, label = paste(culture, round(avgViews, digits=2), sep="\n"))) +
  scale_size_continuous(range = c(1,4)) +
  labs(fill = "Mean Views", caption = "Source: harvardartmuseums.org/collections/api") + 
  ggtitle("Mean Views of Harvard Art Museum, by Culture") + 
  coord_equal() + theme_void() + guides(size=FALSE, colour=FALSE) +
 ggsave("./graphs/culture_views_cloud10.png")

circles
#grid::grid.raster(logo, x = 0.01, y = 0.01, just = c('left', 'bottom'), width = unit(2, 'cm'))


# ggplotly(circles,tooltip = c("avgViews")) %>% layout(title = list(text = paste0('Mean Views of HAM Works, by Culture',
#                                     '<br>',
#                                     '<sup>',
#                                     'Source: harvardartmuseums.org/collections/api',
#                                     '</sup>')))

### Counts

countData <- data.frame(culture=dfCircle$culture, Count=dfCircle$count) 
 

countPacking <- circleProgressiveLayout(countData$Count, sizetype='area')
countData <- cbind(countData, countPacking)
countDat.gg <- circleLayoutVertices(countPacking, npoints=50)
countDat.gg$Count <- rep(countData$Count, each=51)

countCircles = ggplot() + 
  
  geom_polygon(data = countDat.gg, aes(x, y, group = id, fill=Count, color="D84742")) +
  scale_fill_continuous(high='#D84742', low='#FF9586') +
  
  geom_text(data = countData, aes(x, y, size=Count*5, label = paste(culture, Count, sep="\n"))) +
  scale_size_continuous(range = c(1,4)) +
  labs(fill = "Object Count", caption = "Source: harvardartmuseums.org/collections/api") + 
  ggtitle("Count of Harvard Art Museum Works, by Culture") + 
   guides(size=FALSE, colour=FALSE) +
   coord_equal()   + theme_void() +
  # theme(
  #   plot.title = element_text(size=16),
  #   axis.line=element_blank(),axis.text.x=element_blank(),
  #         axis.text.y=element_blank(),axis.ticks=element_blank(),
  #         axis.title.x=element_blank(),
  #         axis.title.y=element_blank(),
  #         panel.border=element_blank(),panel.grid.major=element_blank(),
  #         panel.grid.minor=element_blank())  
  ggsave("./graphs/culture_count_cloud10.png", width=7, height=7)


countCircles
#grid::grid.raster(logo, x = 0.01, y = 0.01, just = c('left', 'bottom'), width = unit(2, 'cm'))


# ggplotly(countCircles,tooltip = c("Count")) %>% layout(title = list(text = paste0('Count of HAM Works, by Culture',
#                                     '<br>',
#                                     '<sup>',
#                                     'Source: harvardartmuseums.org/collections/api',
#                                     '</sup>')))
```

### Exploratory Plots
More plots for the article, including two boxplots for mean views/ranks per culture.
```{r}
df <- as.data.frame(df)

#Cultures & Count
df$ffculture <- reorder(df$ffculture, df$ffculture, FUN = length)

cultureBar = ggplot(data =df, aes(x = ffculture, fill=..count..)) + geom_bar() + 
  labs(y = "Occurrences Per Culture", x = "Cultures", title = "Cultures of Harvard Art Museum Works") +
  scale_y_continuous(breaks=seq(0,7000,1000)) +
  scale_fill_continuous(high='#D84742', low='#FF9586') + theme(legend.position="none") +
   theme(plot.title = element_text(size=16)) +
  ggsave("./graphs/culture_count_bar_graph.png")
cultureBar
#grid::grid.raster(logo, x = 0.01, y = 0.01, just = c('left', 'bottom'), width = unit(1, 'cm'))
  


#Culture vs Views
cultureviews <- aggregate(df$views, by = list(df$ffculture), FUN = mean)
colnames(cultureviews) <- c("Culture", "Views")
cultureviews <- cultureviews[order(cultureviews$Views),]
cultureviews$Culture <- factor(cultureviews$Culture, levels = cultureviews$Culture)
cultureViews = ggplot(data = cultureviews, aes(x= Culture, y = Views, fill=Views)) + geom_bar(stat = "identity") + 
  labs(y = "Average Views Per Culture", title = "Average Views Per Culture of HAM Works") +
    scale_fill_continuous(high='#D84742', low='#FF9586') + theme(legend.position="none") +
   theme(plot.title = element_text(size=16)) +
   scale_y_continuous(breaks=seq(0,40,5)) +
  ggsave("./graphs/culture_view_bar_graph.png")
cultureViews
#grid::grid.raster(logo, x = 0.01, y = 0.01, just = c('left', 'bottom'), width = unit(1, 'cm'))

#Dot Plot
#dotPlot = ggplot(cultureviews, aes(x=Culture, y=Views)) + 
#  geom_point(col = '#ee3838', size=3, aes(color=Culture)) +   # Draw points, col = '#EE3838
  #scale_color_manual(values=rep(primary,each=2)) +
#  geom_segment(aes(x=Culture, 
#                   xend=Culture, 
#                   y=min(Views), 
#                   yend=max(Views)), 
#               linetype="dashed", 
#               size=0.1) +   # Draw dashed lines
#  labs(title="Average Views Per Culture of Harvard Art Museum Works", 
#       x = "Average Views",
#       subtitle="", 
#       caption="") +  
#     theme(plot.title = element_text(size=14)) +
#  coord_flip() +
#ggsave("./graphs/culture_view_dot_graph.png")
#dotPlot
#grid::grid.raster(logo, x = 0.01, y = 0.01, just = c('left', 'bottom'), width = unit(1, 'cm'))
```


#### Boxplots
From this section, we only used the colorful violinplots, comparing against logviews and rank.
```{r}

#ggplot(df, aes(x=ffculture, y=views)) +
#  geom_boxplot()

# relevelling for convenience
df$ffculture <- factor(df$ffculture, 
    levels = c("Japanese", "Other", "Italian", "British",  "Greek", "French", "German", "Roman","American", "Unknown"))

# VIEWS & VIOLIN PLOT
viewsViol = ggplot(df, aes(x=ffculture, y=logviews)) +
  geom_violin(aes(fill=ffculture), color=NA, alpha=0.8) + 
  labs(y = "Log Views", x = "Cultures", title = "Cultures & Log Views of Harvard Art Museum Works") +
  stat_summary(fun=median, geom="point", size=2, color="#4B5973") +
  theme(plot.title = element_text(size=17)) +
  theme(legend.position="none") +
  ggsave("./graphs/culture_views_violin_graph.png")
viewsViol
#grid::grid.raster(logo, x = 0.01, y = 0.01, just = c('left', 'bottom'), width = unit(1, 'cm'))
  


#culture vs ranks: boxplots
cultureranks <- aggregate(df$rank, by = list(df$ffculture), FUN = mean)
colnames(cultureranks) <- c("Culture", "Ranks")
cultureranks <- cultureranks[order(cultureranks$Ranks),]
cultureranks$Culture <- factor(cultureranks$Culture, levels = cultureranks$Culture)
#ggplot(data = cultureranks, aes(x= Culture, y = Ranks)) + geom_bar(stat = "identity") + 
#  labs(y = "Average Ranks Per Culture", title = "Boxplot of Average Ranks Per Culture")


# culture and rank boxplots
#df$ffculture <- factor(df$ffculture, 
#    levels = c("Japanese", "Greek", "Roman", "Other", "American", "German", "Unknown", "British", "Italian", "French"))
#ggplot(df, aes(x=ffculture, y=rank)) +
#  geom_boxplot() + scale_y_reverse() + labs(y = "Rank", x = "Culture",
#  title = "Boxplots of Culture Ranks")

#  RANK & VIOLIN PLOT
# right order is c("Japanese", "Other", "Italian", "British",  "Greek", "French", "German", "Roman","American", "Unknown")
df$ffculture <- factor(df$ffculture, 
    levels = c("Japanese", "Other", "Italian", "British",  "Greek", "French", "German", "Roman","American", "Unknown"))
rankViol = ggplot(df, aes(x=ffculture, y=rank)) +
  geom_violin(aes(fill=ffculture), color=NA, alpha=0.8) + labs(y = "Object Rank", x = "Culture",
  title = "Culture & Object Ranks of Harvard Art Museum Works") +
    stat_summary(fun=median, geom="point", size=2, color="#4B5973") +
  theme(plot.title = element_text(size=16)) +
  scale_fill_discrete(name = "Culture") +
  theme(legend.position="none") +
  ggsave("./graphs/culture_rank_violin_graph.png")

rankViol

#grid::grid.raster(logo, x = 0.01, y = 0.01, just = c('left', 'bottom'), width = unit(1, 'cm'))

```